Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-13 paper/tv.tex
m

\usepackage{xcolor}
\usepackage[thicklines]{cancel}
\renewcommand{\CancelColor}{\color{lightgray}}

@@

  \vspace{-1mm}

@@

\begin{wrapfigure}{R}{0.5\columnwidth}
    \vspace{-3mm}
\centering
\includegraphics[width=0.5\columnwidth]{verification.png}
        \vspace{-3mm}
\caption{\label{fig:Verification_oberview}System Overview.}
      \vspace{-1mm}
\end{wrapfigure}

An overview of our automated verification system is given in \figref{fig:Verification_oberview} It consists of a Hoare-style forward verifier and a TRS. 
The inputs of the forward verifier are HipHop.js programs annotated with temporal specifications written in \timedEffects (cf. \figref{fig:overview_coffee}).

The input of the TRS is a pair of effects LHS and RHS, referring to the inclusion LHS \code{\CONTAIN} RHS to be checked 
\textit{(LHS refers to left-hand side effects, and RHS refers to right-hand side effects.)}. Besides, the verifier calls the TRS to prove produced inclusions, i.e., between the effects states and pre/post conditions or assertions (cf. \figref{fig:forward_example}). The TRS will be explained in \secref{sec:Entailment_Prover}.

>>>>

\usepackage{tikz}
\usepackage{xcolor}
\usepackage[thicklines]{cancel}
\renewcommand{\CancelColor}{\color{lightgray}}

@@

  \vspace{-3mm}

@@

\begin{wrapfigure}{R}{0.54\columnwidth}
  \vspace{-3mm}

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-0.65,xscale=0.65]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Rounded Rect [id:dp1113766752673011] 
\draw  [line width=1.5]  (68,142.52) .. controls (68,136.24) and (73.09,131.15) .. (79.37,131.15) -- (216.63,131.15) .. controls (222.91,131.15) and (228,136.24) .. (228,142.52) -- (228,176.63) .. controls (228,182.91) and (222.91,188) .. (216.63,188) -- (79.37,188) .. controls (73.09,188) and (68,182.91) .. (68,176.63) -- cycle ;
%Shape: Rectangle [id:dp6438165442964394] 
\draw  [line width=1.5]  (67,51) -- (287,51) -- (287,104) -- (67,104) -- cycle ;
%Rounded Rect [id:dp29624677487783313] 
\draw  [line width=1.5]  (328,142.52) .. controls (328,136.24) and (333.09,131.15) .. (339.37,131.15) -- (473.63,131.15) .. controls (479.91,131.15) and (485,136.24) .. (485,142.52) -- (485,176.63) .. controls (485,182.91) and (479.91,188) .. (473.63,188) -- (339.37,188) .. controls (333.09,188) and (328,182.91) .. (328,176.63) -- cycle ;
%Shape: Rectangle [id:dp5138829561825217] 
\draw  [line width=1.5]  (309,52) -- (486,52) -- (486,104) -- (309,104) -- cycle ;
%Straight Lines [id:da1612175737893331] 
\draw [line width=1.5]    (137,109) -- (137,127.22) ;
\draw [shift={(137,130.22)}, rotate = 270] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) .. controls (9.04,-1.82) and (4.3,-0.39) .. (0,0) .. controls (4.3,0.39) and (9.04,1.82) .. (14.21,4.28)   ;
%Straight Lines [id:da5383095517878319] 
\draw [line width=1.5]    (428,108) -- (428,127.95) ;
\draw [shift={(428,130.95)}, rotate = 270] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) .. controls (9.04,-1.82) and (4.3,-0.39) .. (0,0) .. controls (4.3,0.39) and (9.04,1.82) .. (14.21,4.28)   ;
%Straight Lines [id:da5450046441977192] 
\draw [line width=1.5]  [dash pattern={on 5.63pt off 4.5pt}]  (229,164.5) -- (275,165.5) -- (325,165.97) ;
\draw [shift={(328,166)}, rotate = 180.54] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) .. controls (9.04,-1.82) and (4.3,-0.39) .. (0,0) .. controls (4.3,0.39) and (9.04,1.82) .. (14.21,4.28)   ;

% Text Node
\draw (61,57) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{113.09pt}\setlength\topsep{0pt}
\begin{center}
Target Program \&\\ Temporal Specifications
\end{center}

\end{minipage}};
% Text Node
\draw (66.57,139.15) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{77.55pt}\setlength\topsep{0pt}
\begin{center}
Hoare-style \\Forward Verifier 
\end{center}

\end{minipage}};
% Text Node
\draw (325,58) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{66.79pt}\setlength\topsep{0pt}
\begin{center}
Two \textit{Timeffs} \\LHS and RHS
\end{center}

\end{minipage}};
% Text Node
\draw (325,139.9) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{79.64pt}\setlength\topsep{0pt}
\begin{center}
Effects Inclusion \\Prover (TRS)
\end{center}

\end{minipage}};
% Text Node
\draw (223.8,117.63) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{51.49pt}\setlength\topsep{0pt}
\begin{center}
Proof \\obligations
\end{center}

\end{minipage}};

\end{tikzpicture}

 %   \vspace{-4mm}
%\centering
%\includegraphics[width=1\columnwidth]{verification.png}
%        \vspace{-3mm}
%\caption{\label{fig:Verification_oberview}System Overview.}
%      \vspace{-1mm}
\caption{\label{fig:Verification_oberview}System Overview.}
\end{wrapfigure}

An overview of our automated verification system is given 
in \figref{fig:Verification_oberview} 
Rounded boxes are the main procedures, and both return \emph{true} 
when the forward reasoning/proving succeeds, return \emph{false} 
otherwise. Rectangular boxes describe the inputs to the procedures.
The input of the TRS is a pair of effects LHS and RHS, referring to the 
inclusion LHS \code{\CONTAIN} RHS to be checked 
\textit{(LHS refers to left-hand-side effects, and RHS refers to right-hand-side 
effects)}. 
Besides, the verifier calls the TRS to prove produced inclusions (dash line). 
The TRS will be explained in \secref{sec:Entailment_Prover}.
